Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-19 WSSSPE2_report/WSSSPE2_review.tex
Format. No changes.

\item \textbf{Robert Downs: Community Recommendations for Improving Sustainable
Scientific Software Practices.}
Robert Downs, of the Columbia University Center for International Earth
Science Information Network (CIESIN), 
%presented Community Recommendations for
%Improving Sustainable Scientific Software Practices (2014), and 
described a
focus group study conducted with W. Christopher Lenhardt, Erin Robinson, Ethan Davis, and Nicholas
Weber of the Science Software Cluster (SSC) of the Federation of Earth Science Information Partners (ESIP). For the study, almost 300 attendees of the 2014 Summer ESIP Meeting were
invited to participate in simultaneous roundtable discussions on  
sustainability of science software. Over two-thirds of the roundtable focus
groups   responded to a semi-structured survey that contained
three sets of questions eliciting recommendations for near-term actions of the
community to improve sustainable software practices. Initial analysis of the participants' responses to the questionnaire
 revealed several suggestions, which  included improving community engagement and collaborative
activities, increasing understanding and awareness, and creating incentives to
motivate sustainable science software practices. 
%Based on the recommendations
%offered by the focus group respondents for near-term actions, 
The ESIP SSC plans to engage the community %to achieve progress in the near future 
in the recommended activities for improving sustainable scientific
software practices.

@@

\item \textbf{Alice Allen: Find it! Cite it!}
%
The Astrophysics Source Code Library (ASCL) is an online registry of
scientist-written software used in astronomy research. Their primary interest is
rendering research more transparent by making this software more discoverable for
examination. The ASCL is treated as a publication by an indexing resource for
astronomy, the Astrophysics Data System (ADS). ADS tracks citations to what it
indexes, including citations to ASCL entries. Increasing rewards for writing
software, whether through citation, transitive credit or other methods, gives
software authors a powerful reason to take the time to build sustainability into
their software and is an excellent way to drive community change. 
\begin{comment}The ASCL
actively looks for opportunities to use change management strategies to move
astronomy to a more transparent discipline; these strategies can be used in
other disciplines to further change in them. 
\end{comment}
\end{enumerate}

>>>>

\item \textbf{Robert Downs: Community Recommendations for Improving Sustainable
Scientific Software Practices.}
Robert Downs, of the Columbia University Center for International Earth
Science Information Network (CIESIN), 
%presented Community Recommendations for
%Improving Sustainable Scientific Software Practices (2014), and 
described a
focus group study conducted with %W. Christopher Lenhardt, Erin Robinson, Ethan
% Davis, and Nicholas Weber of 
the Science Software Cluster (SSC) of the
Federation of Earth Science Information Partners (ESIP). For the study, almost
300 attendees of the 2014 Summer ESIP Meeting were invited to participate in
simultaneous roundtable discussions on sustainability of science software. Over
two-thirds of the roundtable focus groups responded to a semi-structured survey
that contained three sets of questions eliciting recommendations for near-term
actions of the community to improve sustainable software practices. Initial
analysis of the
participants' responses to the questionnaire revealed several suggestions, which
included improving community engagement and collaborative activities, increasing
understanding and awareness, and creating incentives to motivate sustainable
science software practices.
%Based on the recommendations
%offered by the focus group respondents for near-term actions, 
The ESIP SSC plans to engage the community %to achieve progress in the near future 
in the recommended activities for improving sustainable scientific
software practices.

@@

\item \textbf{Alice Allen: Find it! Cite it!}
%
The Astrophysics Source Code Library (ASCL) is an online registry of
scientist-written software used in astronomy research. Their primary interest is
rendering research more transparent by making this software more discoverable for
examination. The ASCL is treated as a publication by an indexing resource for
astronomy, the Astrophysics Data System (ADS). ADS tracks citations to what it
indexes, including citations to ASCL entries. Increasing rewards for writing
software, whether through citation, transitive credit or other methods, gives
software authors a powerful reason to take the time to build sustainability into
their software and is an excellent way to drive community change.

\begin{comment}
The ASCL actively looks for opportunities to use change management strategies to
move astronomy to a more transparent discipline; these strategies can be used in
other disciplines to further change in them.
\end{comment}
\end{enumerate}
